%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Publication}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

%---------------------------------------------------------
  \cventryPub
    {\textbf{Jaemin Choi}} % Authors
    {Formal Verification of Chase-Lev Deque in Concurrent Separation Logic} % Paper
    {2023} % Year
    {
      \textit{MS Thesis.}
      \begin{cvitems}
        \item[]
        \item Formal proof of the correctness of concurrent Chase-Lev work-stealing deque.
        \item To my knowledge, the first formal verification of Chase-Lev deque that (1) is mechanized in a proof assistant, (2) uses a realistic \& unrestrictive implementation, and (3) proves a strong specification.
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventryPub
    {Jaehwang Jung, Janggun Lee, \textbf{Jaemin Choi}, Jaewoo Kim, Sunho Park, Jeehoon Kang} % Authors
    {Modular Verification of Safe Memory Reclamation in Concurrent Separation Logic} % Paper
    {2023} % Year
    {
      Submitted to \textit{ACM SIGPLAN conference on Object-oriented Programming, Systems, Languages, and Applications (OOPSLA) 2023.}
      \begin{cvitems}
        \item[]
        \item Formally verified modular specification of hazard pointers and RCU, making it easy to extend a data structure's verification to use safe memory reclamation (SMR) schemes.
        \item I helped verify the SMR schemes, and verified Chase-Lev deque with SMR.
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventryPub
    {Hoang-Hai Dang, Jaehwang Jung, \textbf{Jaemin Choi}, Duc-Than Nguyen, William Mansky, Jeehoon Kang, Derek Dreyer} % Authors
    {Compass: Strong and Compositional Library Specifications in Relaxed Memory Separation Logic} % Paper
    {2022} % Year
    {
      \textit{ACM SIGPLAN conference on Programming Languages Design and Implementation (PLDI) 2022.}
      \begin{cvitems}
        \item[]
        \item Framework for strong specifications of data structures in relaxed memory model.
        \item I verified Treiber's stack with the Compass specification.
        \item Available at: \href{https://dl.acm.org/doi/10.1145/3519939.3523451}{https://dl.acm.org/doi/10.1145/3519939.3523451}
      \end{cvitems}
    }

%---------------------------------------------------------

\end{cventries}
